\textbf{Characterizing Errors and Uncertainties in NEMD Simulations of Phonon Transport}

### 2018-04-11 Slides/r1/md_si.tex
..

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{decorations.fractals}
%\usepackage{lmodern}
\usepackage{animate}
\usepackage{movie15}
\usepackage{bm}
\usepackage{pifont}
\usepackage{empheq}
\usepackage[many]{tcolorbox}
\usepackage{smartdiagram}
\usepackage[customcolors]{hf-tikz}
\usepackage{dashrule} % for dotted vertical line
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{pigment}{rgb}{0.2, 0.2, 0.6}
%\usepackage{flexisym}

@@

% Custom block environment
% Custom block environment
\newenvironment<>{varblock}[2][.9\textwidth]{%
  \setlength{\textwidth}{#1}
  \begin{actionenv}#3%
    \def\insertblocktitle{#2}%
    \par%
    \usebeamertemplate{block begin}}
  {\par%
    \usebeamertemplate{block end}%
  \end{actionenv}}

@@

@@

%\vspace{-5mm}
\begin{center}
\begin{figure}[htbp]
        \includegraphics[width=0.9\textwidth]{./Figures/schematic}
\end{figure}
\vspace{3mm}
%        \animategraphics[autopause,poster=first,loop,height=0.60\textwidth]{5}
%        {./animation/snap}{0}{64}
\end{center}
\end{column}
\end{columns}

@@

\begin{empheq}[box=\tcbhighmath]{align}
  \kappa = \frac{q}{\left|\frac{dT}{dx}\right|} \nonumber
\end{empheq}

@@

\section{\scshape Discrepancy}
\subsection{response}
\begin{frame}{Response Surface: Discrepancy}

@@

\begin{itemize}
\myitem PC representation of the discrepancy, 
$\epsilon_{\mbox{\tiny{d}}}$:

\begin{empheq}[box=\tcbhighmath]{align}
\epsilon_{\mbox{\tiny{d}}} \approx \mathcal{\epsilon}_{\mbox{\tiny{d}}}^{\mbox{\tiny{PCE}}} = 
\sum_{\bm{k}\in\mathcal{I}} c_{\bm{k}}(T)\Psi_{\bm{k}}(\bm{\xi(\theta)})
\nonumber
\end{empheq}

@@

>>>>

%% General document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{mindmap}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations.fractals}
%\usepackage{lmodern}
\usepackage{animate}
\usepackage{movie15}
\usepackage{bm}
\usepackage{pifont}
\usepackage{empheq}
\usepackage[many]{tcolorbox}
\usepackage{smartdiagram}
\usepackage[customcolors]{hf-tikz}
\usepackage{dashrule} % for dotted vertical line
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{pigment}{rgb}{0.2, 0.2, 0.6}
\DeclareMathOperator*{\argmin}{arg\,min}
%\usepackage{flexisym}

@@

\setbeamertemplate{blocks}[rounded][shadow=false]
\addtobeamertemplate{block begin}{\pgfsetfillopacity{0.8}}{\pgfsetfillopacity{1}}
\setbeamercolor{structure}{fg=mygreen}
\setbeamercolor*{block title example}{fg=blue!50,
bg= blue!10}
\setbeamercolor*{block body example}{fg= blue,
bg= blue!5}

@@

\vspace{7mm}
\begin{center}
\begin{tikzpicture}[mindmap, grow cyclic, every node/.style=concept, concept color=orange!40, 
    level 1/.append style={level distance=5cm,sibling angle=90},
    level 2/.append style={level distance=3cm,sibling angle=45},transform canvas={scale=0.5}]

    \node{Non-Equlibrium Molecular Dynamics}
   child [concept color=blue!30]{ node {Noise}
        child { node {Experiment Data}}
        child { node {MD Simulation}}
    }
    child [concept color=yellow!30]{ node {Model Inadequacy}
    child { node {Upscaling}}
        child { node {Missing Physics}}
    }
    child [concept color=green!30]{ node {Inter-atomic Potential}
        child { node {Potential Selection}}
        child { node {Parameter Values}}
         }
    child [concept color=red!30]{ node {Simulation Set-up}
        child { node {System Size}}
        child { node {Heat flux/Thermal gradient}}
        child { node {Duration}}
    };

  \end{tikzpicture}
  \end{center}

@@

%\vspace{-5mm}
\begin{center}
\begin{figure}[htbp]
        \includegraphics[width=0.9\textwidth]{./Figures/schematic}
\end{figure}
\vspace{3mm}
        \animategraphics[autoplay,poster=first,loop,height=0.60\textwidth]{5}
        {./animation/snap}{0}{64}
\end{center}
\end{column}
\end{columns}

@@

\begin{center}
\begin{tcolorbox}[width=0.3\textwidth,height=0.2\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\kappa = \frac{q}{\left|\frac{dT}{dz}\right|} \nonumber
\ee
\end{tcolorbox}
\end{center}

%\begin{empheq}[box=\tcbhighmath]{align}
%  \kappa = \frac{q}{\left|\frac{dT}{dz}\right|} \nonumber
%\end{empheq}

@@

\section{\scshape Response Surface}
\subsection{response}
\begin{frame}{Response Surface: Discrepancy}

@@

\begin{itemize}
\myitem PC representation of the discrepancy, 
$\epsilon_{\mbox{\tiny{d}}}$:
\vspace{-2mm}

\begin{center}
\begin{tcolorbox}[width=0.9\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\scriptsize
\be
\epsilon_{\mbox{\tiny{d}}} \approx \mathcal{\epsilon}_{\mbox{\tiny{d}}}^{\mbox{\tiny{PCE}}} = 
\sum_{\bm{k}\in\mathcal{I}} c_{\bm{k}}(T)\Psi_{\bm{k}}(\bm{\xi(\theta)})
 \nonumber
\ee
\end{tcolorbox}
\end{center}

\vspace{2mm}
\normalsize

\myitem Uncertain parameters, $\bm{\theta}$:~$\{L,\frac{dT}{dz}\}$
\scriptsize
\begin{center}
$L~\sim~\mathcal{U}[50a, 100a](\angstrom)$ \\ \vspace{2mm}
$\frac{dT}{dz}~\sim~\mathcal{U}[\frac{1.5}{a}, \frac{2.5}{a}](\frac{K}{\angstrom})$

\end{center}

@@

\subsection{response}
\begin{frame}{Verification}

\begin{columns}
\begin{column}{0.5\textwidth}
\vspace{-1mm}
\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.8\textwidth]{./Figures/err2D_s}
  \end{figure}
\end{center}
%\vspace{-2mm}
\scriptsize

\begin{center}
\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\scriptsize
\be
 \varepsilon_{\tiny{\mbox{L-2}}} = \frac{\left[\sum_{j}(\epsilon_{\tiny{\mbox{d},j}}^{\mbox{\tiny{MD}}} - 
 \epsilon_{\tiny{\mbox{d},j}}^{\mbox{\tiny{PCE}}})^2\right]^{\frac{1}{2}}}{\left[\sum_j(\epsilon_{\tiny{\mbox{d},j}}
 ^{\mbox{\tiny{MD}}})^2\right]^{\frac{1}{2}}} \sim \mathcal{O}(10^{-3}) \nonumber
 \ee
\end{tcolorbox}
\end{center}

\begin{center}
\begin{figure}[htbp]
\vspace{-3mm}
  \includegraphics[width=0.8\textwidth]{./Figures/err2D_300}
  \\ \tiny{300~K} \vspace{1mm} \\
  \includegraphics[width=0.8\textwidth]{./Figures/err2D_500}
  \\ \tiny{500~K}
\end{figure}
\end{center}

\subsection{response}
\begin{frame}{Direct Method}

\begin{columns}
\begin{column}{0.5\textwidth}
\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.85\textwidth]{./Figures/kinv_300}
  \\ \vspace{1mm} \tiny{300~K}
  \end{figure}
\end{center}
\end{column}
\hspace{-6mm}
\begin{column}{0.5\textwidth}
\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.85\textwidth]{./Figures/kinv_500}
   \\ \vspace{1mm}\tiny{500~K}
  \end{figure}
\end{center}
\end{column}

\end{columns}

\vspace{2mm}
\begin{itemize}
\myitem y-intercept of the straight line fit  to the above plot provides an estimate of the bulk thermal conductivity. 
\end{itemize}
\end{frame}

\section{\scshape Potential}
\subsection{sw}

\begin{frame}{The Stillinger-Weber Potential}

\scriptsize
\vspace{10mm}
\tikz[overlay, remember picture] \node at (2.9,1) {
\begin{tcolorbox}[width=0.34\textwidth,colback=DeepSkyBlue4,notitle,colframe=DeepSkyBlue4,colupper=white]
\textsc{Functional Form}
\end{tcolorbox}
};
\tikz[overlay, remember picture] \node at (5.3,-0.16) {
\begin{tcolorbox}[width=0.8\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\Phi(1,\ldots,N) = \sum\limits_{i,j(i<j)}v_{ij}^{(2)}(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}v_{ij}^{(3)}(\lambda,\gamma)\nonumber
\ee
\end{tcolorbox}
};
\normalsize

\vspace{15mm}
\textsc{Shortcomings}

\begin{itemize}
\myitem {\color{pigment}Inadequate} functional representation. 
\vspace{1mm}
\myitem Estimates based on a {\color{pigment}limited} search. 
\vspace{1mm}
\myitem Do not account for {\color{pigment}measurement error} and {\color{pigment}MD noise}. 
\vspace{1mm}
\myitem {\color{pigment}Parametric uncertainties} were not considered. 
\end{itemize}

\subsection{sw}

\begin{frame}{The Stillinger-Weber Potential}

\scriptsize
\vspace{10mm}
\tikz[overlay, remember picture] \node at (2.9,1) {
\begin{tcolorbox}[width=0.34\textwidth,colback=DeepSkyBlue4,notitle,colframe=DeepSkyBlue4,colupper=white]
\textsc{Functional Form}
\end{tcolorbox}
};
\tikz[overlay, remember picture] \node at (5.3,-0.16) {
\begin{tcolorbox}[width=0.8\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\Phi(1,\ldots,N) = \sum\limits_{i,j(i<j)}v_{ij}^{(2)}(A,B,p,q,\alpha)\hspace{1mm}+\sum\limits_{i,j,k(i<j<k)}v_{ij}^{(3)}(\lambda,\gamma)\nonumber
\ee
\end{tcolorbox}
};
\normalsize

\vspace{15mm}
\textsc{Mitigation Strategies}

\begin{itemize}
\myitem {\color{pigment}Sensitivity Analysis} of the parameters. 
\vspace{1mm}
\myitem {\color{pigment}Forward propagation} of the uncertainty. 
\vspace{1mm}
\myitem {\color{pigment}Bayesian calibration} of the key parameters.
\end{itemize}

\section{Sensitivity}
\subsection{sense}

\begin{frame}{Sensitivity Analysis}

\begin{columns}
\begin{column}{0.55\textwidth}
\textsc{Challenges}

\vspace{2mm}
\begin{itemize}

\Myitem Global sensitivity analysis is {\color{pigment}computationally intractable}.
\vspace{2mm}
\Myitem Perturbing potential parameters $\rightarrow$ loss of {\color{pigment}structural integrity}. 
\end{itemize}
\end{column}

\begin{column}{0.45\textwidth}
\begin{center}
%\begin{figure}[htbp]
 % \includegraphics[width=0.85\textwidth]{./Figures/unstable}
 % \end{figure}
  \animategraphics[autopause,poster=first,loop,height=0.90\textwidth]{5}
       {./anim_unstable/snap}{0}{49}

  \end{center}

\subsection{sense}

\begin{frame}{Sensitivity Analysis}
\begin{itemize}
\myitem Derivative-based sensitivity measures (DGSM) are estimated to identify \textit{unimportant} parameters.

\hspace{-5mm}
\tikz[overlay, remember picture] \node at (2,-1) {
\scriptsize
\begin{tcolorbox}[width=0.27\textwidth,colback=red!20,notitle,colframe=red!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\be
\hspace{-4.2mm}
\mu_i = \mathbb{E}\left[\left(\frac{\partial G(\bm{\theta})}{\partial \theta_i}\right)^{2}\right] \hspace{4mm} \rightarrow \nonumber
\ee
\end{tcolorbox}
};

\hspace{-5mm}
\tikz[overlay, remember picture] \node at (5.56,-0.5) {
\scriptsize
\begin{tcolorbox}[width=0.20\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\be
\hspace{-4.5mm}
\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}  \hspace{2mm}\rightarrow \nonumber
\ee
\end{tcolorbox}
};

\hspace{-5mm}
\tikz[overlay, remember picture] \node at (8.6,0) {
\scriptsize
\begin{tcolorbox}[width=0.25\textwidth,colback=green!20,notitle,colframe=green!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\be
\hspace{-3mm}
\mathcal{T}_i \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})   \nonumber
\ee
\end{tcolorbox}
};

\vspace{12mm}

\myitem DGSM estimates are used to compute upper bound on Sobol total effect index~($\mathcal{T}_i$).

\subsection{sense}

\begin{frame}{Sensitivity Analysis}
\vspace{2mm}

\myitem Add an NPT ensemble prior to NVT and run it for a sufficiently long time. 
\vspace{2mm}

\begin{center}
{\color{gray}NPT} \hspace{5mm} $\rightarrow$ \hspace{5mm} {\color{green}NVT} \hspace{5mm} $\rightarrow$ \hspace{5mm} 
{\color{cyan}NVE} \hspace{5mm}
$\rightarrow$ \hspace{5mm} {\color{magenta}NVE}
\\ \vspace{1mm}
\tiny [Relax system length] \hspace{1mm}[Eqilibrate system to 300 K] \hspace{1mm} [Equilibrate thermostats] \hspace{4mm}
 [Generate Data]
\\ \vspace{1mm}

\tiny{N: Number of Atoms~~~P: Pressure~~~V: Volume~~~T: Temperature~~~E: Energy}
\end{center}

\begin{center}
\vspace{-2mm}
\begin{figure}[htbp]
  \includegraphics[width=0.6\textwidth]{./Figures/lx_npt}
  \end{figure}
\end{center}

\subsection{sense}

\begin{frame}{Parameter Screening}

\begin{algorithm}[H]
\SetAlgoLined
\scriptsize
\texttt{Generate $n_1$ points in $\mathbb{R}^{d}$.}\;
\nonl\scriptsize\texttt{\color{blue}$\%~d$: Number of parameters}\;
\texttt{Perturb each point along the $d$ directions to obtain a set of $n_1(d+1)$ points.}\;
\texttt{Compute $\mu_i$ using model evaluations at the $n_1(d+1)$}\;
\texttt{Determine initial ranks, $\mathcal{R}^{old}$ based on $\hat{\mathcal{C}_i\mu_i}$ values for $\theta_i$}\;
\texttt{Set $k$ = 1}\;
%\nonl\scriptsize\texttt{\color{blue}$\%~k$: Iteration counter}\;
\Repeat{($\mathcal{R}^{\tiny{new}}$ $\neq$ $\mathcal{R}^{\tiny{old}}$ {\bf or}  
               $max\_pdev$~$>~\tau$)}{
\texttt{Generate $n_k$ new points in $\mathbb{R}^{d}$.}\;
\texttt{Perturb each point along the $d$ directions to obtain a set of $n_k(d+1)$ points.}\;
\texttt{Compute and store model evaluations at the $n_k(d+1)$ points.}\;
\texttt{Compute $\mu_i$ using prior model evaluations at $(d+1)(n_1 + \sum_j^k n_j)$ points.}\;
\texttt{Determine new ranks, $\mathcal{R}^{new}$ based on updated $\hat{\mathcal{C}_i\mu_i}$ values.}\;
\texttt{Compute $max\_pdev$ = max$\left(\frac{|\mu_{i,k} - \mu_{i,k-1}|}{ \mu_{i,k-1}}\right)$.}\;
\nonl\scriptsize\texttt{\color{blue}$\%~max\_pdev$: Maximum percentage deviation in $\mu_i$ between successive iterations.}\;
\texttt{Set $k$ = $k$ + 1}\;
}
\end{algorithm}

\subsection{sense}

\begin{frame}{Parameter Screening}

\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.7\textwidth]{./Figures/ub}
  \end{figure}
\end{center}

\section{\scshape Surrogate}
\subsection{sur}

\begin{frame}{Reduced Order Surrogate}

\myitem PCE for $\kappa$:

\scriptsize
\begin{center}
\begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\kappa  = \sum\limits_{\bm{s}\in\mathcal{A}} c_{\bm{s}}(T)\Psi_{\bm{s}}(\bm{\xi})\nonumber
\ee
\end{tcolorbox}
\vspace{1mm} 
\tiny {$\bm{\xi}:~\{\xi_1(A),\xi_2(q),\xi_3(\alpha),\xi_4(\lambda),\xi_5(\gamma)\}$}
\end{center}

\normalsize
\vspace{2mm}
\myitem Regularized least-squares minimization problem:

\scriptsize
\begin{center}
\begin{tcolorbox}[width=1.2\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\hspace{-3mm}
\hat{\bm{c}} = \argmin\limits_{\bm{c}\in \mathbb{R}^{|\mathcal{A}|}}\mathbb{E}\left[\left(\bm{c}^{\tiny{\mbox{T}}}\Psi(\bm{\xi(\theta)}) - 
\kappa_{\bm{\theta}}^{\tiny{\mbox{MD}}}\right)^2\right]~+~\lambda\|\bm{c}\|_1 \nonumber
\ee
\end{tcolorbox}
\end{center}

\begin{column}{0.5\textwidth}
\vspace{-11mm}
\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=1.0\textwidth]{./Figures/PCE5D_eloo}
  \end{figure}
\end{center}

\subsection{sur}

\begin{frame}{Verification}

\begin{columns}
\begin{column}{0.6\textwidth}
\textsc{L-2 Norm}
\vspace{5mm}
\begin{center}
\scriptsize
\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\hspace{-5mm}
\epsilon_{\mbox{\tiny{L-2}}} = 
\frac{\left[\sum\limits_{i=1}^{N=25}\left(\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)}) - 
\mathcal{M}^{PCE}(\bm{\theta}_{\mbox{\tiny{5D}}}^{(i)})\right)^{2}\right]^{\frac{1}{2}}}{\left[\sum_{i=1}^{N}
\left(\mathcal{M}(\bm{\theta}_{\mbox{\tiny{7D}}}^{(i)})\right)^2\right]^{\frac{1}{2}}} \rightarrow \mathcal{O}(10^{-2})
\nonumber
\ee
\end{tcolorbox}
\end{center}

\hspace{3mm}
\begin{column}{0.4\textwidth}
\hspace{5mm}\textsc{Probabilistic}

\begin{center}
\begin{figure}[htbp]
\hspace{12mm}
  \includegraphics[width=0.95\textwidth]{./Figures/PCE5D_kde}
  \end{figure}
\end{center}

\subsection{sur}

\begin{frame}{Global Sensitivity Analysis}

\begin{columns}
\begin{column}{0.5\textwidth}
\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.9\textwidth]{./Figures/PCE5D_gsa}
  \\ \scriptsize{10$^{6}$ samples}
  \end{figure}
\end{center}
\end{column}
\hspace{-9mm}
\begin{column}{0.5\textwidth}
\begin{center}
\begin{figure}[htbp]
  \includegraphics[width=0.9\textwidth]{./Figures/ub}
    \\ \scriptsize{25 samples}
  \end{figure}
\end{center}
\end{column}

\end{columns}
\end{frame}

\section{\scshape Bayes}
\subsection{bayes}

\begin{frame}{Bayesian Calibration}

\begin{columns}
\begin{column}{0.55\textwidth}
\begin{itemize}
\myitem Bayes' rule:

\begin{center}
\scriptsize
\begin{tcolorbox}[width=0.7\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-2mm}
\be
\mathcal{P}(\bm{X}\vert \bm{Y}) \propto \mathcal{P}(\bm{Y}\vert\bm{X})\mathcal{P}(\bm{X})
\nonumber
\ee
\end{tcolorbox}
\vspace{1mm}
\tiny{$\bm{X}:\{\alpha,\gamma\}$}
\end{center}

\myitem Likelihood, $\mathcal{P}(\bm{Y}\vert\bm{X})$:
\begin{center}
\scriptsize
\begin{tcolorbox}[width=1.1\textwidth,colback=DeepSkyBlue!20,notitle,colframe=DeepSkyBlue!20,colupper=DeepSkyBlue4]
\vspace{-3mm}
\be
\mathcal{P}(\bm{Y}\vert\bm{X}) = \frac{1}{\sqrt{2\pi\sigma^2}}\exp\left[-\frac{(\kappa_{\tiny{\mbox{E}}} - 
\kappa_{\tiny{\mbox{MD}}})^2}{2\sigma^2}\right]
\nonumber
\ee
\end{tcolorbox}
\end{center}

\hspace{3mm}
\begin{column}{0.45\textwidth}

\begin{center}
\vspace{-20mm}
\begin{figure}[htbp]
\hspace{3mm}
  \includegraphics[width=1.0\textwidth]{./Figures/gl}
  \end{figure}
\end{center}

%\subsection{conc}

\begin{frame}{Concluding Remarks}
